---
title: "bachelor"
author: "Liv & Ane"
date: "2024-10-22"     
output: html_document  
--- 

## VIGTIGT - tjek inden afleverer 
**HUSK at kopiere det andre plot-chunks ind her de rigtige steder HVIS vi ændrer title, y-akse mm.)!!!!
           
   
  
# Setup & loading data

```{r setup, include=FALSE}  
# Setup
knitr::opts_chunk$set(echo = TRUE)  
```

```{r}
# Loading packages
library(pacman)
p_load(tidyverse, ggplot2, dplyr, reshape2, RColorBrewer, ggpubr,lme4,lmerTest, tidyr, dplyr, emmeans, nnet, patchwork, cowplot, MASS,car) 
```

```{r} 
# Loading data  
df <- read.csv("data_4dec.csv", sep = ";", header = TRUE)  
```

# Cleaning data

```{r}
# Renaming columns 
df <- df %>%
  rename(test = "A101", id = "A103_01", age = "CC05_20", education_level = "CC06", consent = "BB03", 
         
         any_mental_disorder = "CC14", which_mental_disorder = "CC15", depression = "CC15_01", anxiety ="CC15_02", ocd ="CC15_03", adhd_add = "CC15_04", autism ="CC15_05", schizophrenia ="CC15_06", ptsd = "CC15_07", other_disorders ="CC15_08", answer_round = "BB08", answer_again = "EE01",
         
         which_hc = "CC02", on_off_hc = "CC17", type_of_COC = "CC09", days_since_last_period = "CC19_01", time_on_hc ="CC20", hc_less_three_months ="CC20_06", hc_three_to_six_months ="CC20_01", hc_six_to_year ="CC20_02", hc_one_to_two_years ="CC20_03", hc_two_to_five_years ="CC20_04", hc_more_than_10_years ="CC20_05", hc_five_to_ten_years = "CC20_07", which_hc_before = "CC24", hc_before_yn = "CC21", type_of_COC_before = "CC23", how_long_since_hc_before = "CC22", active_inactive_hc = "CC25",
         
         empathy_q2 = "DD07_20", empathy_q3_r = "DD07_21", empathy_q4_r = "DD07_01", empathy_q6 ="DD07_02", empathy_q8 = "DD07_03", empathy_q9 = "DD07_04", empathy_q10 = "DD07_05", empathy_q11 = "DD07_06", empathy_q13_r = "DD07_07", empathy_q14_r = "DD07_08", empathy_q15_r = "DD07_09", empathy_q17 = "DD07_10", empathy_q18_r = "DD07_11", empathy_q19_r = "DD07_12", empathy_q20 = "DD07_13", empathy_q21 = "DD07_14", empathy_q22 = "DD07_15", empathy_q24 = "DD07_16", empathy_q25 = "DD07_17" , empathy_q27 = "DD07_18", empathy_q28 = "DD07_19", 
         
         mood_slider = "FF06_01", wellbeing_q1 = "FF07_01", wellbeing_q1 = "FF07_01", wellbeing_q2 = "FF07_02", wellbeing_q3 = "FF07_03", wellbeing_q4 = "FF07_04", wellbeing_q5 = "FF07_05",
         
         track_period = "CC10", regular_period = "CC11", period_phase = "CC18", time_sum = "TIME_SUM")
```

```{r}
# Changing the id's to lower case 
df$id <- as.factor(df$id)  
df$id <- tolower(df$id)   
```

```{r}
# Turn all NA values into 1 in the column answer_round 
df$answer_round[is.na(df$answer_round)] <- 1

# Overview of the three answer rounds
table(df$answer_round)  
```


# Exclusion criterias    

```{r}
# Removing cases where...  

# Mood-rating is not answered 
df <- df %>% filter(!is.na(mood_slider)) 

# Contraceptive implant   
df <- df %>% filter(which_hc != 7 | is.na(which_hc))

# Vaginal ring
df <- df %>% filter(which_hc != 4 | is.na(which_hc))

# Contraceptive patch
df <- df %>% filter(which_hc != 5 | is.na(which_hc))

# Contraceptive injection
df <- df %>% filter(which_hc != 6 | is.na(which_hc))

# Participants who don't track their period
df <- df %>% filter(track_period != 3 | is.na(track_period))

# Participants who don´t know which period phase
df <- df %>% filter(period_phase != 5 |  is.na(period_phase)) 

# If more than 35 days since last period 
df <- df %>% filter(days_since_last_period <35 | is.na(days_since_last_period))

# Removing answers that are 1 or 2 (where 1 is less than a month and two is 1-3 months) 
df <- df %>% filter(!(how_long_since_hc_before %in% c(1, 2)) | is.na(how_long_since_hc_before)) 

# Removing HC under 3 months (2 means checked off)
df <- df%>% filter(hc_less_three_months !=2 | is.na(hc_less_three_months)) 
```


```{r}
# Seeing how many answered it one, two and three times
table(df$answer_round)   
 
# Removing second and third round answers
df <- df %>% filter(answer_round == 1)

# IMPORTANT NOTE: to see the results including all three rounds, the code line above can be commented out and the analysis can be carried out by including minor changes in the model, suggested by the comments
```
   
 
```{r}
# Checking that only the first answer round is present in df 
table(df$answer_round)  
```
  
## Checking distribition of the responses    

```{r}
# Checking the distribution of HC types 
table(df$which_hc) # 1 is COC here
 
# Checking the distribution of NC cycle phases  
table(df$period_phase)   
```
 
```{r}
# Number of participants on HC and not on HC (NC) 
hc_n <- sum(df$on_off_hc == 2, na.rm = TRUE)  
hc_y <- sum(df$on_off_hc == 1, na.rm = TRUE)  
cat("Number of participants on HC:", hc_y, "\n")
cat("Number of participants not on HC:", hc_n, "\n") 

# Number of responses per specific value in column CC02/which_hc   
antal_1 <- sum(df$which_hc == 1, na.rm = TRUE)  
antal_2 <- sum(df$which_hc == 2, na.rm = TRUE)
antal_3 <- sum(df$which_hc == 3, na.rm = TRUE)  
    
# Showing the results   
cat("Number of participants on COC:", antal_1, "\n")
cat("Number of participants on LNG-IUD:", antal_2, "\n")
cat("Number of participants on POP:", antal_3, "\n")   
``` 
```{r}
# Overview of the participants' level of education  
a_1 <- sum(df$education_level == 1, na.rm = TRUE) 
a_2 <- sum(df$education_level == 2, na.rm = TRUE) 
a_3 <- sum(df$education_level == 3, na.rm = TRUE)
a_4 <- sum(df$education_level == 4, na.rm = TRUE)
a_5 <- sum(df$education_level == 5, na.rm = TRUE)
a_6 <- sum(df$education_level == 6, na.rm = TRUE)    

# Showing the results    
cat("Number of responses for 1 (Elementary school):", a_1, "\n")
cat("Number of responses for 2 (High School/vocational qualification):", a_2, "\n")
cat("Number of responses for 3 (2-2½ years,short further education):", a_3, "\n")
cat("Number of responses for 4 (3-4 years, medium-cycle higher education):", a_4, "\n")
cat("Number of responses for 5 (5-6 years,long further education):", a_5, "\n")
cat("Number of responses for 6 (PhD):", a_6, "\n")
```
 
```{r}
# Overview of the participants' with mental disorders and not with disorders 
an_1 <- sum(df$any_mental_disorder == 1, na.rm = TRUE) 
an_2 <- sum(df$any_mental_disorder == 2, na.rm = TRUE) 
an_3 <- sum(df$any_mental_disorder == 3, na.rm = TRUE)

# Showing the results   
cat("Number of participants who ARE currently diagnosed with a mental health disorder:", an_1, "\n")
cat("Number of participants who are NOT diagnosed with a mental health disorder:", an_2, "\n")
cat("Number of participants who don't want to answer this question:", an_3, "\n")
```

```{r}
# Overview of the participants' different mental disorders
an_4 <- sum(df$depression == 2, na.rm = TRUE) # 2 = checked
an_5 <- sum(df$anxiety == 2, na.rm = TRUE)
an_6 <- sum(df$ocd == 2, na.rm = TRUE)   
an_7 <- sum(df$adhd_add == 2, na.rm = TRUE)
an_8 <- sum(df$autism == 2, na.rm = TRUE)
an_9 <- sum(df$schizophrenia == 2, na.rm = TRUE)   
an_10 <- sum(df$ptsd == 2, na.rm = TRUE) 
an_11 <- sum(df$other_disorders == 2, na.rm = TRUE)   

# Showing the results   
cat("Number of participants with depression:", an_4, "\n")
cat("Number of participants with an anxiety disorder:", an_5, "\n")
cat("Number of participants with OCD:", an_6, "\n")
cat("Number of participants with ADHD/ADD:", an_7, "\n")
cat("Number of participants with Autism:", an_8, "\n")
cat("Number of participants with Schizophrenia:", an_9, "\n")
cat("Number of participants with PTSD:", an_10, "\n") 
cat("Number of participants with another disorder:", an_11, "\n")
```

# Preparing analysis   
  
## Calculate empathy scores (r after empathy = reversed)

```{r}
# In all empathy scores, change 1 to 0, 2 to 1, 3 to 2, 4 to 3, 5 to 4, 6 to 5.
df <- df %>% 
  mutate(across(starts_with("empathy_q"), ~ recode(.x, `1` = 0, `2` = 1, `3` = 2, `4` = 3, `5` = 4)))
 
# Reverse the scores with r in the end
df <- df %>%
  mutate(across(ends_with("_r"), ~ recode(.x, `0` = 4, `1` = 3, `2` = 2, `3` = 1, `4` = 0))) 

# Add a new column with empathy score by using sum
df$empathy_score <- rowSums(df[, c("empathy_q2", "empathy_q3_r", "empathy_q4_r", "empathy_q6", "empathy_q8", "empathy_q9", "empathy_q10", "empathy_q11", "empathy_q13_r", "empathy_q14_r", "empathy_q15_r", "empathy_q17", "empathy_q18_r", "empathy_q19_r", "empathy_q20", "empathy_q21", "empathy_q22", "empathy_q24", "empathy_q25", "empathy_q27", "empathy_q28")], na.rm = TRUE)   
```

## Calculate the well-being scores 

```{r}
# Reverse scores so that 1 becomes 5, 2 becomes 4, 3 becomes 3, 4 becomes 2, 5 becomes 1, 6 becomes 0 
df <- df %>%
  mutate(wellbeing_q1 = recode(wellbeing_q1, `1` = 5, `2` = 4, `3` = 3, `4` = 2, `5` = 1, `6` = 0)) 

# Add new column with well-being score by using sum 
df$wellbeing_score <- rowSums(df[, c("wellbeing_q1", "wellbeing_q2", "wellbeing_q3", "wellbeing_q4", "wellbeing_q5")], na.rm = TRUE)
```

## Add correct/incorrect  

```{r}
# Changing the rows in emotion recognition task columns, to either 1 (correct answer) or 0 (incorrect answers) 
df_correct <- df %>%
  mutate(AA13 = ifelse(AA13 == 3, 1, 0),
         AA16 = ifelse(AA16 == 5, 1, 0),
         AA17 = ifelse(AA17 == 6, 1, 0),
         AA18 = ifelse(AA18 == 4, 1, 0),
         AA15 = ifelse(AA15 == 2, 1, 0),
         AA14 = ifelse(AA14 == 1, 1, 0),
         AA19 = ifelse(AA19 == 1, 1, 0),
         AA20 = ifelse(AA20 == 2, 1, 0),
         AA21 = ifelse(AA21 == 3, 1, 0),
         AA22 = ifelse(AA22 == 6, 1, 0),
         AA23 = ifelse(AA23 == 4, 1, 0),
         AA24 = ifelse(AA24 == 5, 1, 0),
         AA25 = ifelse(AA25 == 1, 1, 0),
         AA26 = ifelse(AA26 == 2, 1, 0),
         AA27 = ifelse(AA27 == 3, 1, 0),
         AA28 = ifelse(AA28 == 6, 1, 0),
         AA29 = ifelse(AA29 == 4, 1, 0),
         AA30 = ifelse(AA30 == 5, 1, 0),
         AA31 = ifelse(AA31 == 1, 1, 0),
         AA32 = ifelse(AA32 == 2, 1, 0),
         AA33 = ifelse(AA33 == 3, 1, 0),
         AA34 = ifelse(AA34 == 6, 1, 0),
         AA35 = ifelse(AA35 == 4, 1, 0),
         AA36 = ifelse(AA36 == 5, 1, 0),
         AA37 = ifelse(AA37 == 1, 1, 0),
         AA38 = ifelse(AA38 == 2, 1, 0),
         AA39 = ifelse(AA39 == 3, 1, 0),
         AA40 = ifelse(AA40 == 6, 1, 0),
         AA41 = ifelse(AA41 == 4, 1, 0),
         AA42 = ifelse(AA42 == 5, 1, 0),
         AA43 = ifelse(AA43 == 1, 1, 0),
         AA44 = ifelse(AA44 == 2, 1, 0),
         AA45 = ifelse(AA45 == 3, 1, 0),
         AA46 = ifelse(AA46 == 6, 1, 0),
         AA47 = ifelse(AA47 == 4, 1, 0),
         AA48 = ifelse(AA48 == 5, 1, 0),
         AA49 = ifelse(AA49 == 1, 1, 0),
         AA50 = ifelse(AA50 == 2, 1, 0),
         AA51 = ifelse(AA51 == 3, 1, 0),
         AA52 = ifelse(AA52 == 6, 1, 0),
         AA53 = ifelse(AA53 == 4, 1, 0),
         AA54 = ifelse(AA54 == 5, 1, 0),
         AA55 = ifelse(AA55 == 1, 1, 0),
         AA56 = ifelse(AA56 == 2, 1, 0),
         AA57 = ifelse(AA57 == 3, 1, 0),
         AA58 = ifelse(AA58 == 6, 1, 0),
         AA59 = ifelse(AA59 == 4, 1, 0),
         AA60 = ifelse(AA60 == 5, 1, 0),
         AA61 = ifelse(AA61 == 1, 1, 0),
         AA62 = ifelse(AA62 == 2, 1, 0),
         AA63 = ifelse(AA63 == 3, 1, 0),
         AA64 = ifelse(AA64 == 6, 1, 0),
         AA65 = ifelse(AA65 == 4, 1, 0),
         AA66 = ifelse(AA66 == 5, 1, 0),
         AA67 = ifelse(AA67 == 1, 1, 0),
         AA68 = ifelse(AA68 == 2, 1, 0),
         AA69 = ifelse(AA69 == 3, 1, 0),
         AA70 = ifelse(AA70 == 6, 1, 0),
         AA71 = ifelse(AA71 == 4, 1, 0),
         AA72 = ifelse(AA72 == 5, 1, 0))



# Adding a correct-answers column for emotion recognition task
df_correct$sum_correct <- rowSums(df_correct[, c("AA13", "AA16", "AA17", "AA18", "AA15", "AA14", "AA19", "AA20", "AA21", "AA22", "AA23", "AA24", "AA25", "AA26", "AA27", "AA28", "AA29", "AA30", "AA31", "AA32", "AA33", "AA34", "AA35", "AA36", "AA37", "AA38", "AA39", "AA40", "AA41", "AA42", "AA43", "AA44", "AA45", "AA46", "AA47", "AA48", "AA49", "AA50", "AA51", "AA52", "AA53", "AA54", "AA55", "AA56", "AA57", "AA58", "AA59", "AA60", "AA61", "AA62", "AA63", "AA64", "AA65", "AA66", "AA67", "AA68", "AA69", "AA70", "AA71", "AA72")], na.rm = TRUE)
```

 
## Name the stimuli columns 

```{r}
# Name the stimuli columns
df_emotions_correct <- df_correct %>% rename(
    hap_20_m = "AA13",
    sur_20_m = "AA16",
    fea_20_m = "AA17",
    sad_20_m = "AA18",
    dis_20_m = "AA15",
    ang_20_m = "AA14",
    ang_20_f = "AA19",
    dis_20_f = "AA20",
    hap_20_f = "AA21",
    fea_20_f = "AA22",
    sad_20_f = "AA23",
    sur_20_f = "AA24",
    ang_40_m = "AA25",
    dis_40_m = "AA26",
    hap_40_m = "AA27",
    fea_40_m = "AA28",
    sad_40_m = "AA29",
    sur_40_m = "AA30",
    ang_40_f = "AA31",
    dis_40_f = "AA32",
    hap_40_f = "AA33",
    fea_40_f = "AA34",
    sad_40_f = "AA35",
    sur_40_f = "AA36",
    ang_60_m = "AA37",
    dis_60_m = "AA38",
    hap_60_m = "AA39",
    fea_60_m = "AA40",
    sad_60_m = "AA41",
    sur_60_m = "AA42",
    ang_60_f = "AA43",
    dis_60_f = "AA44",
    hap_60_f = "AA45",
    fea_60_f = "AA46",
    sad_60_f = "AA47",
    sur_60_f = "AA48",
    ang_80_m = "AA49",
    dis_80_m = "AA50",
    hap_80_m = "AA51",
    fea_80_m = "AA52",
    sad_80_m = "AA53",
    sur_80_m = "AA54",
    ang_80_f = "AA55",
    dis_80_f = "AA56",
    hap_80_f = "AA57",
    fea_80_f = "AA58",
    sad_80_f = "AA59",
    sur_80_f = "AA60",
    ang_100_m = "AA61",
    dis_100_m = "AA62",
    hap_100_m = "AA63",
    fea_100_m = "AA64",
    sad_100_m = "AA65",
    sur_100_m = "AA66",
    ang_100_f = "AA67",
    dis_100_f = "AA68",
    hap_100_f = "AA69",
    fea_100_f = "AA70",
    sad_100_f = "AA71", 
    sur_100_f = "AA72"
) 
```

 
## More cleaning         

```{r}
# Change the numbers in which hc to the actual names
df_emotions_correct$which_hc <- recode(df_emotions_correct$which_hc, "1" = "COC", "2" = "LNG-IUD", "3" = "POP")

# Change the phases to the actual names, 1 = MP, 2 = LFP, 4 = OP, 3 = LP, 5 = I don't know
df_emotions_correct$period_phase <- recode(df_emotions_correct$period_phase, "1" = "MP", "2" = "LFP", "4" = "OP", "3" = "LP", "5" = "dont_know")
   

# Create a new column that combines 'which_hc' and 'period_phase'
df_emotions_correct$combined_hc_phase <- ifelse(!is.na(df_emotions_correct$which_hc), 
                                    df_emotions_correct$which_hc, 
                                    df_emotions_correct$period_phase) 

df_emotions_correct$type_of_COC <- recode(df_emotions_correct$type_of_COC, "1" = "mono", "2" = "multi", "3" = "dont_know")


# Convert the new combined column to a factor 
df_emotions_correct$combined_hc_phase <- as.factor(df_emotions_correct$combined_hc_phase)
df_emotions_correct$any_mental_disorder <- as.factor(df_emotions_correct$any_mental_disorder)
df_emotions_correct$which_mental_disorder <- as.factor(df_emotions_correct$which_mental_disorder)
df_emotions_correct$combined_hc_phase <- as.factor(df_emotions_correct$combined_hc_phase)
df_emotions_correct$education_level <- as.factor(df_emotions_correct$education_level)
df_emotions_correct$which_hc <- as.factor(df_emotions_correct$which_hc)
df_emotions_correct$period_phase <- as.factor(df_emotions_correct$period_phase)
df_emotions_correct$age <- as.numeric(df_emotions_correct$age)
```
 
  
# Finding mean and sd for the different groups
 
```{r} 
# Showing participants ages  
table(df$age) 
```

 
```{r} 
# Finding mean age of the groups, HC, no HC (NC), LNG-IUD, COC, POP, MP, LFP, OP, LP

mean(df_emotions_correct$age[df$on_off_hc == 1]) #on HC
sd(df_emotions_correct$age[df$on_off_hc == 1])

mean(df_emotions_correct$age[df$on_off_hc == 2]) #not on HC
sd(df_emotions_correct$age[df$on_off_hc == 2]) 


mean(df_emotions_correct$age[df_emotions_correct$which_hc == "COC"], na.rm = TRUE) #COC
sd(df_emotions_correct$age[df_emotions_correct$which_hc == "COC"], na.rm = TRUE)

mean(df_emotions_correct$age[df_emotions_correct$which_hc == "LNG-IUD"], na.rm = TRUE) #LNG-IUD
sd(df_emotions_correct$age[df_emotions_correct$which_hc == "LNG-IUD"], na.rm = TRUE)

mean(df_emotions_correct$age[df_emotions_correct$which_hc == "POP"], na.rm = TRUE) #POP
sd(df_emotions_correct$age[df_emotions_correct$which_hc == "POP"], na.rm = TRUE)


mean(df_emotions_correct$age[df_emotions_correct$period_phase == "MP"], na.rm = TRUE) #MP
sd(df_emotions_correct$age[df_emotions_correct$period_phase == "MP"], na.rm = TRUE)

mean(df_emotions_correct$age[df_emotions_correct$period_phase == "LFP"], na.rm = TRUE) #LFP
sd(df_emotions_correct$age[df_emotions_correct$period_phase == "LFP"], na.rm = TRUE)

mean(df_emotions_correct$age[df_emotions_correct$period_phase == "OP"], na.rm = TRUE) #OP
sd(df_emotions_correct$age[df_emotions_correct$period_phase == "OP"], na.rm = TRUE)

mean(df_emotions_correct$age[df_emotions_correct$period_phase == "LP"], na.rm = TRUE) #LP
sd(df_emotions_correct$age[df_emotions_correct$period_phase == "LP"], na.rm = TRUE)
```

```{r}
# Finding mean and sd for population
mean(df_emotions_correct$age) 
sd(df_emotions_correct$age) 
```


## Calculate sum for each emotion (for control regressions) 

```{r} 
# Calculate the sum for each emotions

# sum_hap  
df_emotions_correct$sum_hap <- rowSums(df_emotions_correct %>% select(starts_with("hap_")), na.rm = TRUE)

# sum_ang
df_emotions_correct$sum_ang <- rowSums(df_emotions_correct %>% select(starts_with("ang_")), na.rm = TRUE)

# sum_dis
df_emotions_correct$sum_dis <- rowSums(df_emotions_correct %>% select(starts_with("dis_")), na.rm = TRUE)

# sum_fea
df_emotions_correct$sum_fea <- rowSums(df_emotions_correct %>% select(starts_with("fea_")), na.rm = TRUE)

#sum_sad 
df_emotions_correct$sum_sad <- rowSums(df_emotions_correct %>% select(starts_with("sad_")), na.rm = TRUE)

# sum_sur
df_emotions_correct$sum_sur <- rowSums(df_emotions_correct %>% select(starts_with("sur_")), na.rm = TRUE)
```


## Calculate sum for each intensity

```{r}
# Calculate the sum for each intensity 

# Intensity 20%
df_emotions_correct$sum_20 <- rowSums(df_emotions_correct %>% select(contains("_20_")), na.rm = TRUE)

# Intensity 40%
df_emotions_correct$sum_40 <- rowSums(df_emotions_correct %>% select(contains("_40_")), na.rm = TRUE)

# Intensity 60%
df_emotions_correct$sum_60 <- rowSums(df_emotions_correct %>% select(contains("_60_")), na.rm = TRUE)

# Intensity 80%
df_emotions_correct$sum_80 <- rowSums(df_emotions_correct %>% select(contains("_80_")), na.rm = TRUE)

# Intensity 100%
df_emotions_correct$sum_100 <- rowSums(df_emotions_correct %>% select(contains("_100_")), na.rm = TRUE)
```

  
# Finding mean and sd of WHO-5 scores (wellbeing), IRI-scores (empathy) and mood-scores for on/off HC groups

```{r}
#Finding mean and sd of WHO-5 scores, IRI-scores and mood-scores for on/off HC groups

# Mean and sd for WHO-5 scores (on/off HC)

mean(df_emotions_correct$wellbeing_score[df_emotions_correct$on_off_hc == 1]) #on HC
sd(df_emotions_correct$wellbeing_score[df_emotions_correct$on_off_hc == 1]) #on HC

mean(df_emotions_correct$wellbeing_score[df_emotions_correct$on_off_hc == 2]) #off HC
sd(df_emotions_correct$wellbeing_score[df_emotions_correct$on_off_hc == 2]) #off HC


# Mean and sd for IRI scores (on/off HC)

mean(df_emotions_correct$empathy_score[df_emotions_correct$on_off_hc == 1]) #on HC
sd(df_emotions_correct$empathy_score[df_emotions_correct$on_off_hc == 1]) #on HC

mean(df_emotions_correct$empathy_score[df_emotions_correct$on_off_hc == 2]) #off HC
sd(df_emotions_correct$empathy_score[df_emotions_correct$on_off_hc == 2]) #off HC


# Mean and sd for mood scores (on/off HC)

mean(df_emotions_correct$mood_slider[df_emotions_correct$on_off_hc == 1]) #on HC
sd(df_emotions_correct$mood_slider[df_emotions_correct$on_off_hc == 1]) #on HC

mean(df_emotions_correct$mood_slider[df_emotions_correct$on_off_hc == 2]) #off HC
sd(df_emotions_correct$mood_slider[df_emotions_correct$on_off_hc == 2]) #off HC
```


# Statistical analysis

# Control regressions

## Control on education 

```{r} 
# Ensure `education_level` is an ordered factor
df_emotions_correct$education_level <- factor(df_emotions_correct$education_level,
                             levels = c("2", "3", "4", "5"),
                             ordered = TRUE) 

# Ensure `combined_hc_phase` is a nominal (unordered) factor
df_emotions_correct$combined_hc_phase <- factor(df_emotions_correct$combined_hc_phase)

# Fit the ordinal logistic regression model
cm_education <- polr(education_level ~ combined_hc_phase, data = df_emotions_correct, Hess = TRUE)

# Anova test (important that Anova with uppercase A, there is a difference)
Anova(cm_education)
```
  
## Control on the rest    

```{r}
# Control regressions   
cm_empathy <- glm(empathy_score ~ combined_hc_phase, 
               data = df_emotions_correct,  
               family = gaussian) 

cm_wellbeing <- glm(wellbeing_score ~ combined_hc_phase, 
               data = df_emotions_correct,  
               family = gaussian)

cm_mood <- glm(mood_slider ~ combined_hc_phase, 
               data = df_emotions_correct,  
               family = gaussian)      

cm_any_disorder <- glm(any_mental_disorder ~ combined_hc_phase, 
               data = df_emotions_correct,  
               family = binomial)

cm_age <- glm(age ~ combined_hc_phase, 
               data = df_emotions_correct,   
               family = gaussian) 

cm_which_disorder <- multinom(which_mental_disorder ~ combined_hc_phase, 
                data = df_emotions_correct) 


# Checking for statistically significance on control regressions 

# Likelihood ratio test, checks for significance in cm_which_disorder because it is multinom
cm_which_disorder_0 <- multinom(which_mental_disorder~1, data = df_emotions_correct)

anova(cm_which_disorder_0, cm_which_disorder) # p-value is 0.12, which is greater than 0.05 and therefore not significant

# Anova (as omnibustests)  
anova(cm_empathy, test = "F") # this is F-test because family=gaussian
anova(cm_wellbeing, test = "F")
anova(cm_mood, test = "F")
anova(cm_any_disorder, test = "Chisq") # this is chisq-test because family=binomial
anova(cm_age, test = "F")  

# Results
# None of the above control regression models are significant 
```
   
**Results**

```{r}
# overview of the different groups
table(df_emotions_correct$any_mental_disorder, df_emotions_correct$combined_hc_phase)
table(df_emotions_correct$which_mental_disorder, df_emotions_correct$combined_hc_phase)
table(df_emotions_correct$age, df_emotions_correct$combined_hc_phase)
table(df_emotions_correct$which_hc)
table(df_emotions_correct$type_of_COC)
table(df_emotions_correct$active_inactive_hc) 
```
  

# Cleaning 
 
## Changing df to long format

```{r}
#trying to change the data to long format 
df_long <- df_emotions_correct %>% 
  pivot_longer(
    cols = matches("^(hap_|sad_|dis_|ang_|sur_|fea_)"),  
    names_to = "face",
    values_to = "outcome"
  ) %>%
  separate(face, into = c("emotion", "intensity", "gender"), sep = "_")
```

## More cleaning 

```{r}
#changing id, intensity and emotion to factors 
df_long$id <- as.factor(df_long$id)
df_long$intensity <- factor(df_long$intensity, levels = c(20, 40, 60, 80, 100))
df_long$emotion <- as.factor(df_long$emotion)
df_long$on_off_hc <- as.factor(df_long$on_off_hc)

#turn all na values into 1 in the column answer_round
df_long$answer_round[is.na(df_long$answer_round)] <- 1
 
#making the outcome a factor instead of numeric with range from 0-1
df_long$outcome <- as.factor(df_long$outcome)

# Convert the new combined column to a factor 
df_long$combined_hc_phase <- factor(df_long$combined_hc_phase)

# Check the new column 
table(df_long$combined_hc_phase)
```
   
# Step 1: Test our experiment (effect of difficulty) 

```{r}
# Tests whether the intensity makes a difference
m1 <- glmer(outcome ~ intensity + (1|id), 
               data = df_long, 
               family = binomial) 
summary(m1) 
```


# Step 2: test our hypotheses 

## Testing hypotheses 1 and 2 (without intensity and emotion) 

  
### Hypothesis 1: hc vs. natural cycle 

```{r}
# HC vs. cycle 
h1 <- glmer(outcome ~ on_off_hc + (1|id), 
               data = df_long,  
               family = binomial) 
summary(h1)
```


### Hypothesis 2: COC, POP, LNG-IUD vs natural cycle

```{r}
# Testing h2
h234 <- glmer(outcome ~ combined_hc_phase + (1|id), 
               data = df_long, 
               family = binomial)  
  
summary(h234)   
 
# Pairwise comparison
h234_comparisons <- emmeans(h234, pairwise ~ combined_hc_phase)

# View the pairwise contrasts among all emotion levels
print(h234_comparisons$contrasts) 
```
 
## Testing hypotheses 1 and 2 + 3 and 4 (same models as before with intensity and emotion)

### Hypothesis 1 + 3: hc vs. natural cycle, with intensity

```{r}
# HC vs. cycle + intensity 
h1_7 <- glmer(outcome ~ on_off_hc * intensity + (1|id), 
               data = df_long, 
               family = binomial, 
              control = glmerControl(optimizer = "bobyqa")) 

summary(h1_7)
```


# Hypothesis: 2 + 3 (with intensity)  
COC vs cycle, IUD vs COC vs cycle, cycle phase vs cycle phase

```{r}
# h2 with intensity 
h234_7 <- glmer(outcome ~ combined_hc_phase * intensity + (1|id), 
               data = df_long, 
               family = binomial , control = glmerControl(optimizer = "bobyqa"))  

#pairwise comparison
h234_7_comparisons <- emmeans(h234_7, ~ combined_hc_phase * intensity)

# View the pairwise contrasts among all intensity levels
print(h234_7_comparisons$contrasts)  
```


```{r}
contrasts_by_intensity <- contrast(h234_7_comparisons, interaction = "pairwise", by = "intensity") 
print(contrasts_by_intensity)
```


### Hypotese 1 + 4: hc vs. natural cycle, with emotion 

```{r}
# HC vs. cycle + emotion  
h1_6 <- glmer(outcome ~ on_off_hc * emotion + (1|id), 
               data = df_long, 
               family = binomial, 
              control = glmerControl(optimizer = "bobyqa")) 

summary(h1_6)  
```

 
# Hypotese: 2 + 4 (with emotion) 
COC vs cycle, IUD vs COC vs cycle, cycle phase vs cycle phase 

```{r}
# h2 with emotion
h234_6 <- glmer(outcome ~ combined_hc_phase * emotion + (1|id), 
               data = df_long, 
               family = binomial , control = glmerControl(optimizer = "bobyqa"))   
  
#pairwise comparison
h234_6_comparisons <- emmeans(h234_6, ~ combined_hc_phase * emotion)

# View the pairwise contrasts among all emotions
print(h234_6_comparisons$contrasts) 
```


```{r}
contrasts_by_emotion <- contrast(h234_6_comparisons, interaction = "pairwise", by = "emotion")
print(contrasts_by_emotion)
```

